\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{KAHIGIRIZA PETER WARREN \\
16/U/5173/PS\\
216002577
}
\title{RESEARCH ON THE COMMONEST BRAND OF CARS BEING IMPORTED IN UGANDA.}
\begin{document}
	 \begin{center}
		\maketitle \begin{Large}
		{TOPIC DESCRIPTION}
		\end{Large}
	\end{center}
		\begin{flushleft}
		All the cars in Uganda are imported. This is mainly because Uganda lacks the capacity to manufacture or assemble cars. Uganda imports cars from various countries i.e Japan, China, German and the United Kingdom. Some of the commonest car brands imported include; Toyota,Nissan,Mitsubishi,Mercedes Benz.\\
		This is a basic research aimed to find out the commonest brand of cars imported into Uganda. In my analysis, most of these car brands manufacture cars to suit all purposes i.e trucks for heavy duty work, vans and buses for public transport and institutions, minivans for family, station wagons for official purposes, hatchbacks for the average person and sleek sedans for luxury. Importation of cars by importing companies solely depends on the demand of the specific cars on the market. The demand of a specific type of car is caused by many factors for example durability, fuel efficiency, design and purpose of the car. The choice to buy a specific car is dependent on the buyer as some buyers can be irrational. In my discovery, Toyota cars are the commonest brand of car being imported, this is because their make suits well the terrain in Uganda. Other common brands like Mercedes Benz, Mitsubishi and Subaru are a bit more expensive than Toyota but rather common. The market of these cars brands is mainly dominated by the middle class and those slightly above that class.  Other car brands like Subaru are mainly taken up by speed lovers since Subaru specializes in the production of sports cars. Mercedes on the other hand goes straight up for the high-end luxury and it targets the high class citizen.Toyota stands at a great advantage compared to other brands since its spare parts are easier to find locally and the professionals to fix the mechanical problems are readily available. This raises the resale value of Toyota cars and this draws more people to Toyota as their car brand of choice.  
		\end{flushleft}
\end{document}